% !TeX root=../main.tex
% در این فایل، عنوان پایان‌نامه، مشخصات خود و چکیده پایان‌نامه را به انگلیسی، وارد کنید.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\latinuniversity{University of Tehran}
\latincollege{College of Engineering}
\latinfaculty{School of Electrical and }
\latindepartment{Computer Engineering}
\latinsubject{Software Engineering}
\latinfield{Software Engineering}
\latintitle{Accelerating Virtual Network Embedding with Graph Neural Networks}
\firstlatinsupervisor{Prof. Ahmad Khonsari}
%\secondlatinsupervisor{Second Supervisor}
%\firstlatinadvisor{First Advisor}
%\secondlatinadvisor{Second Advisor}
\latinname{Farzad}
\latinsurname{Habibi}
\latinthesisdate{Jan. 2021}
\latinkeywords{Virtual Network Embedding, Graph Neural Networks, Virtualization, Virtual Network}
\en-abstract{
Virtual Network Embedding (VNE) is an essential component of network virtualization technology. 
%
Prior works on VNE mainly focused on resource efficiency and did not address the scalability as a first-grade objective. Consequently, the ever-increasing demand and size render them less-practical.
%
The few existing designs for mitigating this problem either do not extend to multi-resource settings or do not consider the physical servers and network simultaneously.
%
In this work, we develop \ourAlg, a parallelizable VNE solution based on spatial Graph Neural Networks (GNN) that clusters the servers to guide the embedding process towards an improved runtime and performance. 
%
Our experiments using simulations show that the parallelism of \ourAlg\ reduces its runtime by a factor of $8$. Also, \ourAlg\ improves the revenue-to-cost ratio by about $18\%$, compared to other simulated algorithms.
}
